Linking Hypotheses and SI-Paradigms

### 2018-02-14 models/linking hypotheses/linkinghypotheses.rmd

Our linking hypothesis should say something about why an overwhelming majority of individuals would rate an 'XorY' guess to be Right in an ['X','Y'] world state, despite 'XorY' being a suboptimal utterance choice in this world state according to our pragmatic speaker model.

@@

The straw-man linking hypothesis described above was clearly inadequate. But it is a linking hypothesis: it generates predictions about categorical behavior (e.g. responses in the SI-Paradigms experiment) from our model; it "maps the response measure onto the theoretical constructs of interest" (Tanenhaus 2000:564-5). The above hypothesis achieves this by positing that the categorical behavior of interest (answering "Right"/"Wrong"") can be understood as a probabilistic process, whereby the probability that a participant responds "Right" when exposed to utterance u in world state w is equal to the speaker proabibility of u in w as computed by the RSA model:

@@

The above model provides the log odds of responding "Right" vs. "Wrong" as a function of the speaker probability of the utterance being assessed by the participant (in a particular utterance context). It is a better model than the simple straw-man model which assumed a one-to-one correspondance between a) the probability a participant judges some utterance u to be "Right" in w and b) the probability of that utterance u in a world state w, as according to our pragmatic speaker distribution [say more? model comparison?].

@@

Yet another possibility is that for some utterance u in world state w, P("Right"|u,w) is a function of S1'(u|w), where S1' is a transformation of the pragmatic speaker distribution. More specifically, S1' is a renormalized version of S1 after low-probability utterances are filtered from S1 (according to some threshold of probability).

@@

>>>>

Our linking hypothesis should say something about why an overwhelming majority of individuals would rate an 'XorY' guess to be Right in an ['X','Y'] world state, despite 'XorY' being a sub-optimal utterance choice in this world state according to our pragmatic speaker model.

@@

The straw-man linking hypothesis described above was clearly inadequate. But it is a linking hypothesis: it generates predictions about categorical behavior (e.g. responses in the SI-Paradigms experiment) from our model; it "maps the response measure onto the theoretical constructs of interest" (Tanenhaus 2000:564-5). The above hypothesis achieves this by positing that the categorical behavior of interest (answering "Right"/"Wrong"") can be understood as a probabilistic process, whereby the probability that a participant responds "Right" when exposed to utterance u in world state w is equal to the speaker probability of u in w as computed by the RSA model:

@@

The above model provides the log odds of responding "Right" vs. "Wrong" as a function of the speaker probability of the utterance being assessed by the participant (in a particular utterance context). It is a better model than the simple straw-man model which assumed a one-to-one correspondence between a) the probability a participant judges some utterance u to be "Right" in w and b) the probability of that utterance u in a world state w, as according to our pragmatic speaker distribution [say more? model comparison?].

@@

Yet another possibility is that for some utterance u in world state w, P("Right"|u,w) is a function of S1'(u|w), where S1' is a transformation of the pragmatic speaker distribution. More specifically, S1' is a re-normalized version of S1 after low-probability utterances are filtered from S1 (according to some threshold of probability).

@@

```{r}
binary <- add_column(binary, speaker_renorm_probability = 0)

commands <- "speaker_filtered(['X','Y'],0.12)"
code <- paste(model_threshold_2,commands,sep="\n")
speaker_renormprobs_xy <- webppl(code)

commands <- "speaker_filtered(['X'],0.12)"
code <- paste(model_threshold_2,commands,sep="\n")
speaker_renormprobs_x <- webppl(code)

for(i in 1:nrow(binary)){
  for(j in 1:nrow(speaker_renormprobs_xy)){
    if((as.character(speaker_renormprobs_xy[j,]$support) == as.character(binary[i,]$guess_type)) & binary[i,]$card_type == "XY"){
      binary[i,]$speaker_renorm_probability <- speaker_renormprobs_xy[j,]$prob
    }
  }
}

for(i in 1:nrow(binary)){
  for(j in 1:nrow(speaker_renormprobs_x)){
    if((as.character(speaker_renormprobs_x[j,]$support) == as.character(binary[i,]$guess_type)) & binary[i,]$card_type == "X"){
      binary[i,]$speaker_renorm_probability <- speaker_renormprobs_x[j,]$prob
    }
  }
}

l <- glm(as.factor(response) ~ speaker_renorm_probability, data = binary, family = "binomial")
summary(l)
